Multilevel regression models

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2),nAGQ = 5L)
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
  list(
    homclass = "Class-based network homogeneity",
    logrgdpna = "log GDP",
    palmaratio = "Palma Ratio",
    "homclass:palmawd" = "Homogeneity x Palma Ratio",
    top10 = "Share National Income - top 10%",
    "homclass:top10"= "Homogeneity x top 10",
    middle50 = "Share National Income -  bottom 50%",
    "homclass:middle50" = "Homogeneity x bottom 50",
    d10d1 = "Ratio D10/D01",
    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
    giniindex = "Gini (World Bank)",
    "homclass:giniindex" = "Homogeneity x Gini (WB)",
    ttheilge1 = "Theil Index",
    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
  )
texreg::knitreg(models_m,scalebox = 0.75,
                float.pos="h!",                
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save(list = models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save(list = list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
```

>>>>

# Models 
base <- glmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT,family = "binomial"); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-logit-homclass-full-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-logit-homclass-strong-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-logit-homclass-weak-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-ologit-homclass-full-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
  list(
    homclass = "Class-based network homogeneity",
    logrgdpna = "log GDP",
    palmaratio = "Palma Ratio",
    "homclass:palmawd" = "Homogeneity x Palma Ratio",
    top10 = "Share National Income - top 10%",
    "homclass:top10"= "Homogeneity x top 10",
    middle50 = "Share National Income -  bottom 50%",
    "homclass:middle50" = "Homogeneity x bottom 50",
    d10d1 = "Ratio D10/D01",
    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
    giniindex = "Gini (World Bank)",
    "homclass:giniindex" = "Homogeneity x Gini (WB)",
    ttheilge1 = "Theil Index",
    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
  )
texreg::knitreg(models_m,scalebox = 0.75,
                float.pos="h!",                
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-ologit-homclass-strong-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
```

@@

models <- list(homclass,full1,rob1,int_homo)
save( models,file = here::here("output/fullsample-ologit-homclass-weak-individual.RData"))
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
```
